\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/introduction.tex
minor

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

### 2021-03-22 WOOT/Files/related_work.tex
minor

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitations compared with \tool: 
(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

>>>>

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitations compared with \tool: 
(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connectors including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.
